%-------------------------
% Resume in Latex
% Author : Hasan Mahmud (Rhidoy)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
\justifying

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://example.com}{\Large John Doe}} & Email : \href{mailto:example@gmail.com}{example@gmail.com} \\
  \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} & Phone : +1234567890 \\
  \href{https://github.com/johndoe}{github.com/johndoe} \\ City, Country \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Company A}{Kuala Lumpur, Malaysia}
      {Sr. Software Engineer - Full-time}{May 2024 - Now}
      \break
      {Company A is a prominent USA-based financial technology company established in 2013. Access mobile banking, personal finance tools, fast cash advances, and earn cashback rewards for extra funds when needed.}
      \break
      \break
      {I have managed the full system lifecycle from design to deployment, delivering scalable, secure, and high-performance solutions focusing on automation, efficiency, and cloud best practices. Currently, we've few services that have to use \textbf{Go (Golang)}.}
    \resumeSubheading
    {Company B}{Kuala Lumpur, Malaysia}
      {Sr. Software Developer - Contract}{Jan 2023 - May 2024}
      \break
      \underline{\textbf{Work Area:}}
       \resumeItemListStart
       % Project - 01 %
        \item{\textbf{\underline{Project A:}} {I led the design and development of client-centric APIs at Project A, ensuring top-notch code quality and seamless deployments. Utilizing technologies such as \textit{Go (Golang), Microservice, MySQL, Redis, RabbitMQ, Docker, and JavaScript(ReactJS)}, I extended the insurance/takaful coverage to standard motor insurance. My role focused on optimizing the Personal Accident (PA) insurance plan by integrating it with cutting-edge technologies for enhanced functionality and user experience.}}
      % Project - 02 %
        \item{\textbf{\underline{Project B:}} {Contributed to Project B, designing and implementing software solutions for seamless and unrestricted toll collection, improving overall highway user experience. Leveraged \textit{Java(Spring Boot, Spring Cloud), Microservice, MySQL, Redis, Apache Kafka, Docker, and JavaScript(ReactJS)} technologies to achieve project goals effectively.}}
      % Project - 03 %
        \item{\textbf{\underline{Project C:}} {At Project C, led software design and implementation initiatives to improve user experience and system efficiency for diverse industries. Expertise includes \textit{Go (Golang), Microservice, Microsoft SQL Server, Redis, RabbitMQ, Docker, and JavaScript(ReactJS)}.}}
    \resumeItemListEnd

    \resumeSubheading
      {Company C}{Dhaka, Bangladesh}
      {Software Engineer - Full-time}{Feb 2021 - Dec 2022}
      \break
      \underline{\textbf{Work Area:}}
      \resumeItemListStart
        % Project - 01 %
        \item{\textbf{\underline{Project D:}} {As a developer for Project D, specialized in crafting real-time transaction processing software for large financial institutions. Proficient in \textit{Java(Spring Boot, Spring Cloud, Spring Batch), Microservice, Oracle, Redis, RabbitMQ, Docker, Payment Gateway, and JavaScript(ReactJS)}.}}
        % Project - 02 %
        \item{\textbf{\underline{Project E:}} {As a developer for Project E, specialized in crafting real-time transaction processing software for large financial institutions. Proficient in \textit{Java(Spring Boot, Spring Cloud, Spring Batch), Microservice, Oracle, Redis, RabbitMQ, Docker, Payment Gateway, and JavaScript(ReactJS)}.}}
    \resumeItemListEnd
    
    \resumeSubheading
      {Company D}{Dhaka, Bangladesh}
      {Software Engineer - Full-time}{June 2019 - Feb 2021}
      \resumeItemListStart
       \item{\underline{\textbf{Project F:}}}
            {As a developer of Project F, I designed and developed a system that allows the tracking of sales data, inventory levels, and generating reports. It enables users to view real-time data, track sales performance, and manage stock levels efficiently. Technologies: \textit{Java (Spring Boot), JavaScript(React), PostgreSQL, Redis, RabbitMQ, Mockito (Unit testing), Microservice(Spring Cloud), Git, Docker, JPA-Hibernate}.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP SKILLS-----------------
\section{TRAINING SKILLS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Platform A}{City, Country}
      {Programming Instructor}{March 2022 - till}
      \resumeItemListStart
        \item{
        {Conducting a live cohort-based course to teach \textbf{Java and Python Programming, Problem-solving, Database Engineering, and Web Development} to university students and industry professionals.}}\href{https://example.com/course-link}{ [Course Link]}
    \resumeItemListEnd
    \resumeSubheading
      {Platform B}{City, Country}
      {Programming Instructor}{Jan 2023 - till}
      \resumeItemListStart
        \item{
        {Conducting a live cohort-based course to teach} \href{https://example.com/system-design-course}{\textbf{System Design for Software Developer}} {and }\href{https://example.com/leetcode-course}{\textbf{Data Structure and Algorithm with Leetcode Exercise}}}
    \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------Open Source Projects-----------------
\section{Open Source Projects}
  \resumeSubHeadingListStart
    \item{
    \justifying{
      \textbf{\href{https://github.com/exampleuser/automated-attendance-system}{Automated Attendance System}}{: Developed an open-source application for real-time employee attendance tracking using CCTV footage. Contribution included building an optimized machine learning model for human detection and recognition. [Tooling - Machine Learning, Python, Django MVT, Monolithic Architecture]}}
    }
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Software Development Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages}{: Go (Golang), Java, JavaScript, Python}
    }
    \item{
      \textbf{Frameworks and Libraries}{:  Concurrency (Goroutines, Channels, Select), Dependency Management (go mod), Performance Optimization (pprof), Reactive programming}
    }
    \item{
      \textbf{Storage}{: SQL Server, Oracle, MySQL, PostgreSQL and NoSQL (Redis, MongoDB)}\textbf{ Web Server}{: NGINX }
    }
    \item{
      \textbf{DevOps}{: Docker, Kubernetes, \textbf{AWS} (\textbf{EC2}, \textbf{Lambda}, S3, EBS, RDS (MySQL, PostgreSQL), DynamoDB, \textbf{OpenSearch}, \textbf{SQS}, IAM, etc) and Jenkins}
    }
    \item{
      \textbf{Tools}{: Git, Message Broker(RabbitMQ, \textbf{Apache Kafka}), WebHook(Segment), Web Service API (SOAP, RESTful API, GraphQL), Dependency Management (Maven and Gradle), JIRA, Agile Methodologies}
    }
     \item{
      \textbf{Software Architecture}{: \textit{Microservices Architecture}, Event-Driven Architecture}
    }
    
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
     {University A}{City, Country}
      {Master of Science in Computer Science and Technology}{Feb. 2025 -- till}
      \break
      \textbf{Thesis: }\textbf{“A Machine Learning Based Approach for Diabetes Detection and Care in Bangladesh”}{, Gyancity Journal of  Engineering and Technology, Vol.4, No.2, pp.21-28, July 2018 ISSN: 2456-0065 DOI: 10.21058/gjet.2018.42003.  (Denmark)}
  \resumeSubHeadingListEnd


%--------Achievement------------
\section{Achievements}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Contest Achievements}{: 2017, 2015 ACM ICPC Dhaka Region }\textbf{(Honorable Mention)}{, 2016 National Collegiate Programming Contest, Dhaka }\textbf{(Honorable Mention)}{, 2015 Intra Programming Contest }\textbf{(Secure 7th Position)}{, Participated in }\textbf{10+ onsite}{ programming contest and }\textbf{solved more than 1000 problems}{ in several online judge.}
    }
    \item{
      \textbf{Hackathon Competition}{: 2018 Inter University Software and Hardware Carnival }\textbf{(1st Runner-up)}{, 2017 Inter CSE Carnival }\textbf{(4th Position)}
    }
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}